Verifying Demonstrations

### 2017-08-23 properties.tex
Adds discussion of transitivity notion for witness trust

\begin{question}
  How can we do \acp{LP} with 1000s of witnesses each?
  Can we do some preprocessing?
  Ad-hoc networks, broadcast \acp{LP}?
\end{question}
\begin{question}
  Why should anyone trust these witnesses?
  What are the assumptions?
  Signed over a short period of time?\footnote{%
    In a sense, if they collude they have shown support for the cause.
    As long as they are not Sybil it should be fine?
  }
\end{question}
\begin{question}
  Trusted party for the group signatures?
\end{question}
\begin{question}
  Must tie credentials to something unique: phone, phone subscription?
  Cannot register twice, government control?
\end{question}

>>>>

\begin{question}
  Why should anyone trust these witnesses?
  What are the assumptions?
  Signed over a short period of time?\footnote{%
    In a sense, if they collude they have shown support for the cause.
    As long as they are not Sybil it should be fine?
  }
\end{question}

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the blockchain during the protest.
\end{remark}

\begin{question}
  Trusted party for the group signatures?
\end{question}
\begin{question}
  How can we do \acp{LP} with 1000s of witnesses each?
  Can we do some preprocessing?
  Ad-hoc networks, broadcast \acp{LP}?
\end{question}
\begin{question}
  Must tie credentials to something unique: phone, phone subscription?
  Cannot register twice, government control?
\end{question}
